Bucket-Sorted Independent Sets for Algebraic Multigrid

### 2007-09-24 bsis_paper/paper.tex
Typo fix.
git-svn-id: file:///home/rblake/svn/pamg/trunk@30 c7f3fe13-8c30-0410-9127-9a9c42fe009c

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have made two major contributions. First, new
theoretical results were presented expanding knowledge on the nature
of independent-set based coarse-grid selection. Algorithms using the
same rules, with some restrictions, for weight initialization,
independent set slection, and weight update produce the same coarse
grids, regardless of the particular implementation of the
rules. This result decouples the design of policies for selecting
quality coarse grids from the design and efficiency of the algorithms
used to select the coarse grids. The BSIS algorithm is designed as an
example of this. BSIS selects the same coarse grids as CLJP-c, but
uses a more efficient algorithm to select independent sets.

>>>>

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have made two major contributions. First, new
theoretical results were presented expanding knowledge on the nature
of independent-set based coarse-grid selection. Algorithms using the
same rules, with some restrictions, for weight initialization,
independent set selection, and weight update produce the same coarse
grids, regardless of the particular implementation of the
rules. This result decouples the design of policies for selecting
quality coarse grids from the design and efficiency of the algorithms
used to select the coarse grids. The BSIS algorithm is designed as an
example of this. BSIS selects the same coarse grids as CLJP-c, but
uses a more efficient algorithm to select independent sets.
